%
% File acl2020.tex
%
%% Based on the style files for ACL 2020, which were
%% Based on the style files for ACL 2018, NAACL 2018/19, which were
%% Based on the style files for ACL-2015, with some improvements
%%  taken from the NAACL-2016 style
%% Based on the style files for ACL-2014, which were, in turn,
%% based on ACL-2013, ACL-2012, ACL-2011, ACL-2010, ACL-IJCNLP-2009,
%% EACL-2009, IJCNLP-2008...
%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage{times}
\usepackage{latexsym}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepackage{microtype}

\aclfinalcopy 
\setlength\titlebox{5cm}

\newcommand\BibTeX{B\textsc{ib}\TeX}

\title{Group A: Exploration in  Neural Language Model Understanding of Idioms}

\author{Daniel Campos \\
  University of Washington  \\
  Microsoft \\
  \texttt{dacampos@uw.edu} \\\And
  Second Author \\
  Affiliation / Address line 1 \\
  Affiliation / Address line 2 \\
  Affiliation / Address line 3 \\
  \texttt{email@domain} \\}

\date{}

\begin{document}
\maketitle
\section{Introduction}
One or two paragraphs motivating primary research question / hypothesis
● Be specific! (Not “Does BERT understand X?”.)
\section{Methods}
Imagine this as your actual methods section in your final paper.
● What method will you use to address your question?
● What data will you use?
● Pre-existing, generate your own, …
● How will you evaluate?
\section{Possible Results}
● No actual results, but:
● What are the possible outcomes of your experiment?
● What would each outcome show? How would you interpret it?
\section{Division of labor + timeline}
Make a list:
● each task that needs to be accomplished
● Who (can be >1!) will be primarily responsible for it
● Rough estimate of deadline for that step
● Keep in mind: things will change, not go as linearly as planned. But thinking
about these things in advance will help!
● Firm deadlines:
● Presentations of results (mini conference): March 12, last day of class
● Final paper: March 15
● Write concurrently with making presentation
\bibliography{anthology,acl2020}
\bibliographystyle{acl_natbib}
\end{document}
